### 2014-02-19 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Updating model description in dpp manuscript.
Explicitly referring to Bayes' rule and the chain rule of probability in
the initial introduction of the model's posterior.

\begin{linenomath}
With \alignmentVector, \hkyModelVector, \ploidyScalarVector, and
\mutationRateScalarConstantVector in hand, the joint posterior distribution
of our model is given by
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \divTimeMapVector,
        \demographicParamVector, \locusMutationRateScalarVector,
        \locusRateHetShapeParameter, \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\geneTreeVector, \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
        \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)}{
        p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:fullModelCompactJoint}
\end{equation}
which can be expanded out into components that are assumed to be independent
to get
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \hkyModelVector)
        p(\geneTreeVector \given \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\locusMutationRateScalarVector \given \locusRateHetShapeParameter)
        p(\locusRateHetShapeParameter)
        p(\divTimeMapVector)
        p(\demographicParamVector)}{
        p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:fullModelCompact}
\end{equation}
where
$\divTimeMapVector = (\divTimeMap{1}, \ldots, \divTimeMap{\npairs{}})$
is a vector of population divergence times for each of the \npairs{} pairs of
populations,
$\demographicParamVector = (\demographicParams{1}, \ldots,
\demographicParams{\npairs{}})$
is a vector of the demographic parameters for each of the \npairs{} population
pairs,
$\locusMutationRateScalarVector = (\locusMutationRateScalar{1}, \ldots
\locusMutationRateScalar{\nlociTotal})$
is a vector of locus-specific mutation-rate scaling parameters for each of the
\nlociTotal loci,
\locusRateHetShapeParameter is the shape parameter of a gamma-distributed
prior on \locusMutationRateScalar{}, and
$p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
\mutationRateScalarConstantVector)$
is the probability of the data (or the marginal likelihood of the model) given
the fixed constants provided by the investigator.
\end{linenomath}

>>>>

\begin{linenomath}
With \alignmentVector, \hkyModelVector, \ploidyScalarVector, and
\mutationRateScalarConstantVector in hand, the joint posterior distribution
of our model is given by Bayes' rule as
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \divTimeMapVector,
        \demographicParamVector, \locusMutationRateScalarVector,
        \locusRateHetShapeParameter, \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\geneTreeVector, \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
        \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)}{
        p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:fullModelCompactJoint}
\end{equation}
which can be expanded using the chain rule of probability into components that
are assumed to be independent to get
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \hkyModelVector)
        p(\geneTreeVector \given \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\locusMutationRateScalarVector \given \locusRateHetShapeParameter)
        p(\locusRateHetShapeParameter)
        p(\divTimeMapVector)
        p(\demographicParamVector)}{
        p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:fullModelCompact}
\end{equation}
where
$\divTimeMapVector = (\divTimeMap{1}, \ldots, \divTimeMap{\npairs{}})$
is a vector of population divergence times for each of the \npairs{} pairs of
populations,
$\demographicParamVector = (\demographicParams{1}, \ldots,
\demographicParams{\npairs{}})$
is a vector of the demographic parameters for each of the \npairs{} population
pairs,
$\locusMutationRateScalarVector = (\locusMutationRateScalar{1}, \ldots
\locusMutationRateScalar{\nlociTotal})$
is a vector of locus-specific mutation-rate scaling parameters for each of the
\nlociTotal loci,
\locusRateHetShapeParameter is the shape parameter of a gamma-distributed
prior on \locusMutationRateScalar{}, and
$p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
\mutationRateScalarConstantVector)$
is the probability of the data (or the marginal likelihood of the model) given
the fixed constants provided by the investigator.
\end{linenomath}
